---
title: "movie_egalitarianism"
author: "Jing Liu"
date: "11/21/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Data Cleaning
#### Pull the Survey Result from Google Drive, and Shorten the Column Names into Availabe to use. (Finish in Google Drive Excel)
#### Load the Data Sets from Google Drive(export in .csv format) and convert categorical data into corresponding numeric data.
```{r}
survey <- read.csv("/Users/rivertemple/Downloads/movie_egalitarianism.csv", stringsAsFactors = FALSE)
movie <- read.csv("/Users/rivertemple/Downloads/Movie Ratings.csv")
att <- read.csv("/Users/rivertemple/Downloads/attitude.csv")
```
Transform and Remove Unuasable Data of *movie* data set(movie *Sing* was removed during the survey)
```{r}
movie['rate'] <- movie[,1]
movie[,1] <- NULL
names(movie) <- c("movie","rate")
mr <- movie
mrn <- mr[-10,] 
rownames(mrn) <- 1:24
```

Convert Movie Preference (column 5 to 28 in *survey*) by Function
The Criteria is :Scores for movie responses:
Survey Response Score:
“Liked it”= +1
“Didn’t like it” = -1
“Never saw it”=0
Movie score:
Movies that pass = +1
Movies that fail = -1
Subject’s total score = SUM(survey response score* movie score )
```{r}
for (i in 0:23){
    survey[5+i][survey[5+i] == 'Liked it'] <- 1 * mr[1+i,2]
    survey[5+i][survey[5+i] == "Didn't like it"] <- -1 * mr[1+i,2]
    survey[5+i][survey[5+i] == 'Never saw it'] <- 0
    }
```

Adjust the Order of data set *attitude* According to Survey(Move no.9 to no.1)
```{r}
insertRow <- function(existingDF, newrow, r) {
  existingDF[seq(r+1,nrow(existingDF)+1),] <- existingDF[seq(r,nrow(existingDF)),]
  existingDF[r,] <- newrow
  existingDF
}
attn <- insertRow(att, att[9,], 1)
attn2 <- attn[-10,] 
attn2
```

Convert Attitude Categorical Option into Numeric Data
```{r}
for (i in 0:10){
    survey[29+i][survey[29+i] == 'Strongly agree'] <- attn2[1+i,2]
    survey[29+i][survey[29+i] == 'Somewhat agree'] <- attn2[1+i,3]
    survey[29+i][survey[29+i] == 'No opinion'] <- attn2[1+i,4]
    survey[29+i][survey[29+i] == 'Somewhat disagree'] <- attn2[1+i,5]
    survey[29+i][survey[29+i] == 'Strongly disagree'] <- attn2[1+i,6]
}
```

#### Sum Scores for both Movie Preference and Attitude
```{r}
survey[5:39] <- sapply(survey[5:39],as.numeric)
#sapply(survey, class)
survey['movScor'] <- rowSums(survey[,5:28])
survey['attScor'] <- rowSums(survey[,29:39])
```

#### Form *testdf1*, which include *Gender, Religious, Influence, Age, movScor and attScor*.
```{r}
library(knitr)
library(kableExtra)
library(dplyr)
testdf1 <- survey[,c(1:4,40:41)]
testdf1 %>%
  kable(format = "html", caption = "Survey of Movie Preference and Attitude of Egalitarianism") %>%
  kable_styling(font = 20, "bordered", full_width = T)
```

